---
title: "Get started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{get_started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Core functionality

The package is quite small where the core function is `sanityTracker::add_sanity_check` and
a few convenience functions (use the prefix *sc_*) that basically call `sanityTracker::add_sanity_check`.
Some of the convenience functions like `sanityTracker::sc_left_join` perform more than one check
other can check multiple columns at the same time like `sanityTracker::sc_cols_non_NA`.

The most helpful feature is that no matter how deep your sanity check is buried in your source
code, *sanityTracker* will centralize the results AND if the defined check fails a few examples
of the failed rows are stored for investigation. 

The functions are more or less self explanatory, therefore we focus on the stored results and examples.

We start with a very simple check.
```{r}
library(sanityTracker)
sc <- sanityTracker::add_sanity_check(
  fail_vec = mtcars$mpg > 30,
  description = "mpg should be below 30"
)
get_sanity_checks()
```

We see that of the 32 observation contained in *mtcars* 4 have a mpg above 30. It also tracked 
how we actually performed the check in the column *fail_vec_str*. Providing the function also
the data set can be very handy because fails are used to extract examples of failures from the
data set:

```{r}
sc <- sanityTracker::add_sanity_check(
  fail_vec = mtcars$mpg > 30,
  description = "mpg should be below 30. extract example ",
  data = mtcars,
  param_name = "mpg"
)
get_sanity_checks()
```

First note that we now see two lines, where the first is from our initial sanity check. 
Furthermore the second line show now that the column *example* is not empty:

```{r}
get_sanity_checks()[["example"]][[2]]
```

If you call the sanity check from within a function the results also appear in the 
global list of all sanity checks and the table show the function-call where the
check happened.

```{r}
g <- function(x) {
  sanityTracker::add_sanity_check(
    fail_vec = x$mpg > 30,
    description = "mpg should be below 30. check in function",
    data = x,
    param_name = "mpg"
  )
}
f <- function(x) {g(x = x)}
dummy <- f(x = mtcars)
get_sanity_checks()
```

Using `sanityTracker::clear_sanity_checks` to discard all sanity checks that are
currently stored.

```{r}
sanityTracker::clear_sanity_checks()
sanityTracker::get_sanity_checks()
```

# Convenience functions

Doing all checks with `sanityTracker::add_sanity_check` would be cumbersome. Therefore,
the package provides some convenience functions to perform some standard checks, like
are columns *a, b, c, x, y, z* are positive or do not contain missing values or
is their combination unique. All convenience functions start with the prefix *sc_*.
These function provide addition information about the check(s) that they perform in
the column *additional_desc*. So checking that all columns of *mtcars* are positive is 
quite easy.

```{r}
sc <- sanityTracker::sc_cols_positive(
  object = mtcars,
  cols = names(mtcars),
  description = "Exemplary sanity checks"
)
get_sanity_checks()
```


Note that the although the convenience functions do not explicitly list the parameter
*description*, *counter_meas*, *data_name*, *example_size*, *param_name*, *call* and
*fail_callback* can be used via the '...'-argument. 
```{r}
clear_sanity_checks()
sc <- sanityTracker::sc_col_elements(
  object = mtcars,
  col = "carb",
  feasible_elements = 1:4,
  description = "Only usual number of carburetors",
  fail_callback = warning,
  call = "directly from vignette"
)
get_sanity_checks()
```